\newglossaryentry{FRAP}{
    name={FRAP},
    description={\textbf{Fluorescence Recovery After Photobleaching}. A microscopy technique used to study the dynamics of molecular diffusion and protein mobility within cells. The method involves selectively bleaching a fluorescently labeled region using a high-intensity laser and monitoring fluorescence recovery over time as unbleached molecules move into the area. The recovery rate provides insights into molecular diffusion, binding interactions, and membrane fluidity.}
}


\newglossaryentry{phosphoglycerols}{
    name={Phosphoglycerols},
    description={A class of phospholipids derived from glycerol-3-phosphate. They form a major component of biological membranes and typically consist of a glycerol backbone, two fatty acid chains, and a phosphate group attached to a polar head. Examples include phosphatidylcholine and phosphatidylserine.}
}

\newglossaryentry{sphingolipids}{
    name={Sphingolipids},
    description={A class of lipids that contain a sphingosine backbone instead of glycerol. They play crucial roles in cell membrane structure and signaling. Key sphingolipids include ceramides, sphingomyelins, and glycosphingolipids, which are involved in cellular communication and recognition processes.}
}

\newglossaryentry{phosphatidylinositol}{
    name={Phosphatidylinositol (PI)},
    description={A phospholipid that plays a key role in cell signaling and membrane dynamics. It consists of a glycerol backbone linked to two fatty acid chains and a phosphate group attached to an inositol ring. Phosphatidylinositol and its phosphorylated derivatives (phosphoinositides) are involved in intracellular signaling pathways, membrane trafficking, and cytoskeletal organization.}
}


\newglossaryentry{lateralphaseseparation}{
    name={Lateral Phase Separation},
    description={A phenomenon in biological membranes where different lipid and protein components segregate into distinct coexisting phases within the same membrane plane. This separation can lead to the formation of specialized microdomains, such as lipid rafts, which influence membrane fluidity, signaling, and protein localization. Lateral phase separation is driven by differences in lipid composition, temperature, and molecular interactions.}
}

