\newglossaryentry{RNP}{
    name={RNP},
    description={Ribonucleoprotein complex; a molecular complex composed of RNA and proteins that plays key roles in various biological processes such as RNA processing, transport, stability, and translation regulation}
}

\newglossaryentry{P-bodies}{
    name={P-bodies},
    description={Processing bodies; cytoplasmic, membrane-less ribonucleoprotein (RNP) granules involved in mRNA degradation, storage, and translational repression}
}

\newglossaryentry{StressGranules}{
    name={Stress Granules},
    description={Cytoplasmic, membrane-less ribonucleoprotein (RNP) granules that form in response to cellular stress; they store untranslated mRNAs and associated proteins, helping regulate translation and protect RNA during stress conditions}
}

\newglossaryentry{EndoplasmicReticulum}{
    name={Endoplasmic Reticulum (ER)},
    description={A membrane-bound organelle in eukaryotic cells involved in protein and lipid synthesis, calcium storage, and detoxification. It exists in two forms: rough ER (with ribosomes, involved in protein synthesis) and smooth ER (lacking ribosomes, involved in lipid metabolism and detoxification)}
}

\newglossaryentry{BetaOxidation}{
    name={\(\beta\)-oxidation},
    description={A metabolic process that breaks down fatty acids in the mitochondria (and peroxisomes) to generate acetyl-CoA, NADH, and FADH\(_2\), which are used in energy production via the citric acid cycle and oxidative phosphorylation}
}

\newglossaryentry{translocators}{
    name=translocators,
    description={Proteins or protein complexes that transport molecules across biological membranes, such as the cell membrane or organelle membranes. They play a critical role in processes like nutrient uptake, waste export, and protein trafficking}
}

\newglossaryentry{NLS}{
    name={NLS},
    description={Nuclear Localization Signal, a short amino acid sequence that directs the transport of a protein into the nucleus of a cell},
    sort=NLS
}

\newglossaryentry{NPC}{
    name={NPC},
    description={Nuclear Pore Complex, a large protein assembly embedded in the nuclear envelope that regulates the transport of molecules between the nucleus and cytoplasm},
    sort=NPC
}

\newglossaryentry{importin}{
    name={importin},
    description={A transport protein that binds to nuclear localization signals (NLS) on cargo proteins and mediates their transport into the nucleus through the nuclear pore complex (NPC)},
    sort=importin
}

\newglossaryentry{exportin}{
    name={Exportin},
    description={A transport receptor that binds cargo proteins with nuclear export signals (NES) and facilitates their export from the nucleus to the cytosol in a Ran-GTP-dependent manner.}
}

\newglossaryentry{ranGTP}{
    name={Ran-GTP},
    description={The active, GTP-bound form of the Ran protein, primarily found in the nucleus, which facilitates nuclear export by binding to export receptors and releasing import receptors.}
}

\newglossaryentry{ranGDP}{
    name={Ran-GDP},
    description={The inactive, GDP-bound form of the Ran protein, primarily found in the cytosol, which results from the hydrolysis of Ran-GTP and is necessary for recycling import/export receptors.}
}

\newglossaryentry{gef}{
    name={Ran-GEF (Guanine nucleotide exchange factor)},
    description={A nuclear protein that facilitates the exchange of GDP for GTP on Ran, maintaining the high concentration of Ran-GTP in the nucleus.}
}

\newglossaryentry{gap}{
    name={Ran-GAP (GTPase-activating protein)},
    description={A cytosolic protein that stimulates the GTP hydrolysis activity of Ran, converting Ran-GTP to Ran-GDP. This process ensures a high concentration of Ran-GDP in the cytosol, maintaining the Ran-GTP gradient necessary for nuclear transport.}
}

\newglossaryentry{calcineurin}{
    name={Calcineurin},
    description={A calcium/calmodulin-dependent serine/threonine phosphatase that plays a key role in signal transduction. It dephosphorylates nuclear factor of activated T cells (NFAT), enabling its nuclear translocation and regulating immune responses, as well as other cellular processes such as nuclear transport and synaptic plasticity.}
}


\newglossaryentry{cotranslocation}{
    name={co-translational translocation},
    description={A process in which a nascent protein is simultaneously synthesized and translocated into the endoplasmic reticulum (ER) through the Sec61 translocon complex. This occurs co-translationally, meaning the translation of the protein occurs in parallel with its translocation into the ER.}
}

\newglossaryentry{postrtranslocation}{
    name={post-translational translocation},
    description={The process where a protein is synthesized and fully translated in the cytoplasm before being translocated into the endoplasmic reticulum (ER). Unlike co-translocation, post-translocation involves the completion of translation before the protein enters the ER.}
}

\newglossaryentry{translocator}{
    name={translocator (Sec61 complex)},
    description={A protein translocator complex embedded in the membrane of the endoplasmic reticulum (ER). It forms a channel through which nascent polypeptides are co-translationally or post-translationally translocated into the ER lumen or integrated into the membrane. The complex consists of three core subunits: Sec61$\alpha$, Sec61$\beta$, and Sec61$\gamma$.}
}

\newglossaryentry{get3}{
    name={Get3},
    description={An ATPase involved in the Guided Entry of Tail-anchored proteins (GET) pathway. Get3 binds tail-anchored proteins in the cytosol using ATP, protects their hydrophobic C-terminal tail, and targets them to the endoplasmic reticulum (ER) membrane. Upon ATP hydrolysis, it releases the protein for membrane insertion and is then recycled}
}

\newglossaryentry{diochol}{
    name={diochol},
    description={A reduced form of dolichol phosphate, specifically dolichol with two hydroxyl groups instead of a phosphate group. Diochol is involved in the endoplasmic reticulum (ER) glycosylation pathway, where dolichol derivatives serve as lipid carriers for sugar residues during the assembly of glycan chains that are transferred to nascent proteins}
}

\newglossaryentry{calnexin_cycle}{
    name={Calnexin/Calreticulin cycle},
    description={A quality control mechanism in the endoplasmic reticulum (ER) that ensures proper folding of glycoproteins. Calnexin and calreticulin are lectin chaperones that bind to monoglucosylated N-linked oligosaccharides on newly synthesized proteins, facilitating their correct folding. Misfolded proteins are retained in the ER for further processing or degradation},
    sort=CalnexinCalreticulinCycle
}

\newglossaryentry{glucosyltransferase}{
    name={Glucosyltransferase},
    description={An enzyme involved in the Calnexin/Calreticulin cycle that reglucosylates misfolded glycoproteins, allowing them to re-enter the folding cycle. Specifically, it adds a glucose residue to improperly folded glycoproteins, enabling their rebinding to calnexin or calreticulin for further folding attempts},
    sort=Glucosyltransferase
}

\newglossaryentry{mannosidase}{
    name={Mannosidase},
    description={An enzyme that trims mannose residues from N-linked oligosaccharides on glycoproteins in the endoplasmic reticulum. This trimming serves as a signal for targeting misfolded proteins to ER-associated degradation (ERAD) when they fail to achieve proper folding despite multiple attempts},
    sort=Mannosidase
}

\newglossaryentry{LLPS}{
    name={liquid--liquid phase separation (LLPS)},
    description={A biophysical process in which a homogeneous solution of biomolecules (such as proteins and nucleic acids) spontaneously demixes into two distinct liquid phases: a dense, concentrated phase (often droplet-like) and a dilute phase. Driven by multivalent interactions among the molecules, LLPS results in the formation of dynamic, membrane-less compartments within cells}
}

\newglossaryentry{SERCA}{
    name={SERCA pump},
    description={Short for Sarcoplasmic/Endoplasmic Reticulum Calcium ATPase, a membrane-bound P-type ATPase that transports Ca\textsuperscript{2+} from the cytosol into the sarcoplasmic or endoplasmic reticulum using energy from ATP hydrolysis. It plays a critical role in muscle relaxation, calcium signaling, and intracellular calcium homeostasis}
}



