\newglossaryentry{4,5-dihydroototic acid}{
	name={4,5-dihydroototic acid},
	description={An intermediate in pyrimidine biosynthesis formed by the cyclization of carbamoyl aspartic acid via dihydroorotase.}
}

\newglossaryentry{5'-nucleotidase}{
	name={5'-nucleotidase},
	description={An enzyme that hydrolyzes phosphate from nucleotides like AMP during purine degradation.}
}

\newglossaryentry{ATP}{
	name={ATP},
	description={Adenosine triphosphate, the primary energy currency of the cell used to drive many biosynthetic reactions.}
}

\newglossaryentry{Adenosine}{
	name={Adenosine},
	description={A nucleoside formed from adenine and ribose, a breakdown product of AMP that is deaminated to inosine.}
}

\newglossaryentry{Alanine}{
	name={Alanine},
	description={Formed by transamination of pyruvate, catalyzed by alanine transaminase, and involved in nitrogen transport.}
}

\newglossaryentry{Alanine transaminase (ALT)}{
	name={Alanine transaminase (ALT)},
	description={An enzyme that transfers an amino group from glutamate to pyruvate to form alanine, also a liver marker.}
}

\newglossaryentry{Arginine}{
	name={Arginine},
	description={A urea cycle amino acid synthesized from glutamate via a pathway involving acylation, reduction, and conversion through ornithine.}
}

\newglossaryentry{Asparagine}{
	name={Asparagine},
	description={Synthesized from aspartate via amidation by asparagine synthase using glutamine as NH3 donor and ATP.}
}

\newglossaryentry{Asparagine Synthase}{
	name={Aspargine Synthase},
	description={An enzyme that catalyzes the ATP-dependent conversion of aspartate and glutamine into asparagine.}
}

\newglossaryentry{Aspartate}{
	name={Aspartate},
	description={Formed from oxaloacetate by transamination, serves as a precursor for nucleotides and participates in the urea cycle.}
}

\newglossaryentry{Aspartate carbamoyltransferase}{
	name={Aspartate carbamoyltransferase},
	description={An enzyme that catalyzes the condensation of aspartate with carbamoyl phosphate in pyrimidine biosynthesis.}
}

\newglossaryentry{Aspartate transaminase (AST)}{
	name={Aspartate transaminase (AST)},
	description={An enzyme that transfers an amino group to oxaloacetate forming aspartate, used as a liver function marker.}
}

\newglossaryentry{Biogenic amines}{
	name={Biogenic amines},
	description={Low molecular weight amines derived from amino acids, acting as neurotransmitters or hormones.}
}

\newglossaryentry{CTP}{
	name={CTP},
	description={Cytidine triphosphate, synthesized from UTP and used in RNA synthesis and lipid metabolism.}
}

\newglossaryentry{CTP synthetase}{
	name={CTP synthetase},
	description={An enzyme that converts UTP to CTP using glutamine as the nitrogen donor and ATP for energy.}
}

\newglossaryentry{Chemotherapics}{
	name={Chemotherapics},
	description={Drugs that target rapidly dividing cells, often by inhibiting nucleotide biosynthesis (e.g., thymidylate synthesis).}
}

\newglossaryentry{CoA}{
	name={CoA},
	description={Coenzyme A, a cofactor involved in acyl group transfer reactions, derived in part from nucleotide structures.}
}

\newglossaryentry{Creatine}{
	name={Creatine},
	description={A compound derived from glycine, arginine, and methionine, converted into phosphocreatine for ATP regeneration.}
}

\newglossaryentry{Cysteine}{
	name={Cysteine},
	description={An amino acid synthesized from serine and homocysteine via cystathionine, involved in antioxidant synthesis (e.g., glutathione).}
}

\newglossaryentry{DNA}{
	name={DNA},
	description={Deoxyribonucleic acid, the carrier of genetic information built from deoxyribonucleotides.}
}

\newglossaryentry{FAD}{
	name={FAD},
	description={Flavin adenine dinucleotide, a redox cofactor involved in many metabolic reactions.}
}

\newglossaryentry{FMN}{
	name={FMN},
	description={Flavin mononucleotide, a coenzyme derived from riboflavin, functioning in redox reactions.}
}

\newglossaryentry{GTP}{
	name={GTP},
	description={Guanosine triphosphate, a nucleotide used as an energy source and a precursor for RNA.}
}

\newglossaryentry{Glutahione}{
	name={Glutahione},
	description={An antioxidant tripeptide composed of glutamate, cysteine, and glycine, protecting cells from oxidative damage.}
}

\newglossaryentry{Glutamate}{
	name={Glutamate},
	description={An amino acid that acts as a nitrogen donor in biosynthesis and is produced in bacteria from $\alpha$-ketoglutarate and glutamine via glutamate synthase.}
}

\newglossaryentry{Glutamate synthase}{
	name={Glutamate synthase},
	description={An enzyme found in bacteria that converts $\alpha$-ketoglutarate and glutamine into two molecules of glutamate.}
}

\newglossaryentry{Glutamine}{
	name={Glutamine},
	description={A nitrogen-carrying amino acid formed from glutamate and NH4+ by glutamine synthase; serves as a nitrogen donor in many biosynthetic reactions.}
}

\newglossaryentry{Glutamine amidotransferase}{
	name={Glutamine amidotransferase},
	description={An enzyme with two domains that transfers NH3 from glutamine to other molecules, using a glutamyl-enzyme intermediate and ATP-activated acceptors.}
}

\newglossaryentry{Glutamine synthase}{
	name={Glutamine synthase},
	description={An enzyme that catalyzes the ATP-dependent conversion of glutamate and ammonium into glutamine.}
}

\newglossaryentry{Glutathione synthetase}{
	name={Glutathione synthetase},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: Glutathione synthetase.}
}

\newglossaryentry{Glycine}{
	name={Glycine},
	description={A derivative of serine, synthesized by removing a carbon via serine hydroxymethyltransferase using tetrahydrofolate and PLP as cofactors.}
}

\newglossaryentry{Heme}{
	name={Heme},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: Heme.}
}

\newglossaryentry{Methionine}{
	name={Methionine},
	description={An essential amino acid that donates a methyl group in the biosynthesis of creatine and also forms homocysteine in cysteine synthesis.}
}

\newglossaryentry{NAD+}{
	name={NAD+},
	description={Nicotinamide adenine dinucleotide, a coenzyme involved in redox reactions.}
}

\newglossaryentry{NADP+}{
	name={NADP+},
	description={A phosphorylated form of NAD+ used in anabolic redox reactions.}
}

\newglossaryentry{Nucleotides}{
	name={Nucleotides},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: Nucleotides.}
}

\newglossaryentry{PLP}{
	name={PLP},
	description={Pyridoxal phosphate, an active form of vitamin B6 and a coenzyme involved in amino acid metabolism, including transamination and decarboxylation.}
}

\newglossaryentry{Phosphocreatine (Pcr)}{
	name={Phosphocreatine (Pcr)},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: Phosphocreatine (Pcr).}
}

\newglossaryentry{Phosphoribosyltransferases}{
	name={Phosphoribosyltransferases},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: Phosphoribosyltransferases.}
}

\newglossaryentry{Polyamines}{
	name={Polyamines},
	description={Cationic molecules derived from ornithine involved in DNA binding and translational regulation.}
}

\newglossaryentry{Porphyria}{
	name={Porphyria},
	description={A group of diseases caused by defective enzymes in the heme biosynthetic pathway, leading to accumulation of porphyrin intermediates.}
}

\newglossaryentry{Porphyrins}{
	name={Porphyrins},
	description={Heterocyclic macrocycles that coordinate metal ions; precursors to heme.}
}

\newglossaryentry{Proline}{
	name={Proline},
	description={A cyclic derivative of glutamate formed through phosphorylation, reduction, and spontaneous cyclization of glutamate semialdehyde.}
}

\newglossaryentry{Purine}{
	name={Purine},
	description={A nitrogenous base composed of fused imidazole and pyrimidine rings; a building block for DNA and RNA.}
}

\newglossaryentry{Pyrimidine}{
	name={Pyrimidine},
	description={A six-membered nitrogen-containing ring found in cytosine, uracil, and thymine.}
}

\newglossaryentry{RNA}{
	name={RNA},
	description={Ribonucleic acid, a nucleic acid involved in gene expression, composed of ribonucleotides.}
}

\newglossaryentry{Serine}{
	name={Serine},
	description={An amino acid derived from 3-phosphoglycerate (glycolysis intermediate) via oxidation, transamination, and dephosphorylation steps.}
}

\newglossaryentry{Thymidine}{
	name={Thymidine},
	description={A nucleoside component of DNA formed from thymine and deoxyribose, used in salvage pathways.}
}

\newglossaryentry{Thymidine kinase}{
	name={Thymidine kinase},
	description={An enzyme that phosphorylates thymidine to TMP in nucleotide salvage pathways.}
}

\newglossaryentry{Thymidine phosphorylase}{
	name={Thymidine phosphorylase},
	description={An enzyme that salvages thymine by converting it to thymidine using sugar phosphates.}
}

\newglossaryentry{Thymidylate (dTMP)}{
	name={Thymidylate (dTMP)},
	description={A nucleotide synthesized from dUMP by thymidylate synthase; essential for DNA replication.}
}

\newglossaryentry{Uridine phosphorylase}{
	name={Uridine phosphorylase},
	description={An enzyme that adds ribose-1-phosphate to uracil in pyrimidine salvage.}
}

\newglossaryentry{Uridine-cytidine kinase}{
	name={Uridine-cytidine kinase},
	description={An enzyme that phosphorylates uridine and cytidine in salvage pathways.}
}

\newglossaryentry{adenine phosphoribosyltransferases (APRT)}{
	name={adenine phosphoribosyltransferases (APRT)},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: adenine phosphoribosyltransferases (APRT).}
}

\newglossaryentry{adenosine monophosphate (AMP)}{
	name={adenosine monophosphate (AMP)},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: adenosine monophosphate (AMP).}
}

\newglossaryentry{adenylosuccinate lyase}{
	name={adenylosuccinate lyase},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: adenylosuccinate lyase.}
}

\newglossaryentry{alpha-ketobutyrate}{
	name={alpha-ketobutyrate},
	description={A by-product in the synthesis of cysteine from homocysteine and serine, ultimately entering the TCA cycle.}
}

\newglossaryentry{cAMP}{
	name={cAMP},
	description={Cyclic AMP, a second messenger derived from ATP involved in signal transduction pathways.}
}

\newglossaryentry{cGMP}{
	name={cGMP},
	description={Cyclic GMP, a signaling molecule and second messenger involved in cellular responses to hormones.}
}

\newglossaryentry{carbamoyl aspartic acid}{
	name={carbamoyl aspartic acid},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: carbamoyl aspartic acid.}
}

\newglossaryentry{carbamoyl phosphate}{
	name={carbamoyl phosphate},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: carbamoyl phosphate.}
}

\newglossaryentry{cytidine deaminase}{
	name={cytidine deaminase},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: cytidine deaminase.}
}

\newglossaryentry{d-aminolevulinate}{
	name={d-aminolevulinate},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: d-aminolevulinate.}
}

\newglossaryentry{deoxyuridine}{
	name={deoxyuridine},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: deoxyuridine.}
}

\newglossaryentry{dihydroorotase}{
	name={dihydroorotase},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: dihydroorotase.}
}

\newglossaryentry{dihydroorotate oxidase}{
	name={dihydroorotate oxidase},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: dihydroorotate oxidase.}
}

\newglossaryentry{essential amino acids}{
	name={essential amino acids},
	description={Amino acids that cannot be synthesized by the human body and must be obtained from the diet.}
}

\newglossaryentry{folate}{
	name={folate},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: folate.}
}

\newglossaryentry{glutamate-cysteine ligase (GCL)}{
	name={glutamate-cysteine ligase (GCL)},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: glutamate-cysteine ligase (GCL).}
}

\newglossaryentry{guanosine monophosphate}{
	name={guanosine monophosphate},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: guanosine monophosphate.}
}

\newglossaryentry{hypoxanthine}{
	name={hypoxanthine},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: hypoxanthine.}
}

\newglossaryentry{hypoxanthine-guanine phosphoribosyltransferases (HGPRT)}{
	name={hypoxanthine-guanine phosphoribosyltransferases (HGPRT)},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: hypoxanthine-guanine phosphoribosyltransferases (HGPRT).}
}

\newglossaryentry{inosine}{
	name={inosine},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: inosine.}
}

\newglossaryentry{inosine monophosphate (IMP)}{
	name={inosine monophosphate (IMP)},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: inosine monophosphate (IMP).}
}

\newglossaryentry{kinases}{
	name={kinases},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: kinases.}
}

\newglossaryentry{methylmalonyl semialdehyde}{
	name={methylmalonyl semialdehyde},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: methylmalonyl semialdehyde.}
}

\newglossaryentry{neurotransmitter}{
	name={neurotransmitter},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: neurotransmitter.}
}

\newglossaryentry{pyrimidine-nucleoside phosphorylase}{
	name={pyrimidine-nucleoside phosphorylase},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: pyrimidine-nucleoside phosphorylase.}
}

\newglossaryentry{ribonucleotide reductase (RNR)}{
	name={ribonucleotide reductase (RNR)},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: ribonucleotide reductase (RNR).}
}

\newglossaryentry{salvage pathways}{
	name={salvage pathways},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: salvage pathways.}
}

\newglossaryentry{serine hydroxymethyltransferase}{
	name={serine hydroxymethyltransferase},
	description={An enzyme that converts serine to glycine by removing a carbon, requiring tetrahydrofolate and PLP as cofactors.}
}

\newglossaryentry{severe combined immune deficiency (ADA-SCID)}{
	name={severe combined immune deficiency (ADA-SCID)},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: severe combined immune deficiency (ADA-SCID).}
}

\newglossaryentry{succinyl-CoA}{
	name={succinyl-CoA},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: succinyl-CoA.}
}

\newglossaryentry{transamination}{
	name={transamination},
	description={A biochemical process where an amino group is transferred from one molecule (usually glutamate or glutamine) to another, forming new amino acids.}
}

\newglossaryentry{uric acid}{
	name={uric acid},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: uric acid.}
}

\newglossaryentry{uridine}{
	name={uridine},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: uridine.}
}

\newglossaryentry{uridine monophosphate (UMP)}{
	name={uridine monophosphate (UMP)},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: uridine monophosphate (UMP).}
}

\newglossaryentry{uridine triphosphate (UTP)}{
	name={uridine triphosphate (UTP)},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: uridine triphosphate (UTP).}
}

\newglossaryentry{beta-aminoisobutyrate}{
	name={beta-aminoisobutyrate},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: $\beta$-aminoisobutyrate.}
}

\newglossaryentry{beta-ureidopropionase}{
	name={beta-ureidopropionase},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: $\beta$-ureidopropionase.}
}

\newglossaryentry{gamma-glutamylcysteine}{
	name={gamma-glutamylcysteine},
	description={A biochemical term relevant to amino acid or nucleotide metabolism: $\gamma$-glutamylcysteine.}
}

\newglossaryentry{bilirubin}{
    name={bilirubin},
    description={A yellow compound that occurs in the normal catabolic pathway that breaks down heme in red blood cells. It is excreted in bile and urine, and elevated levels may indicate liver dysfunction or disease}
}

\newglossaryentry{tyms}{
    name={thymidylate synthase (TYMS)},
    description={An essential enzyme that catalyzes the conversion of deoxyuridine monophosphate (dUMP) to deoxythymidine monophosphate (dTMP), a key step in DNA synthesis and repair. It is a target for certain anticancer drugs}
}

\newglossaryentry{dihydrofolate_reductase}{
    name={dihydrofolate reductase},
    description={An enzyme that reduces dihydrofolate (DHF) to tetrahydrofolate (THF), a form required for the synthesis of purines, thymidylic acid, and certain amino acids. It plays a critical role in DNA synthesis and cell replication, and is a target of drugs like methotrexate}
}



